\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{STEM Fellowship Big Data Challenge 2020} \\ [10pt] \huge Project Title \\

### 2020-05-23 manuscript/manuscript.tex
fixed formatting

\documentclass[10pt, letterpaper]{article}

@@

% Abstract
\begin{abstract}
    Your abstract will get published whether or not your team wins the challenge, so make sure to do a good job! It should reflect the objectives, methodology and findings of the research project. When writing your abstract, choose the right (amount of) words to convey your information. Avoid long sentences and long-winded explanations as they could make the reader lose focus. The order of your writing is also important. Maintain a logical order to your writing so that the reader links each aspect of your work coherently. Introduction/Background: Explains what problem the study examined and why. You may provide some background to the project, and the motivation behind it. Materials and Methods: Describes the data sources used and methodologies adopted for the data analysis. Key Findings/Results: Outlines the discoveries/what was observed from the analysis. When describing your results, strive to focus on the main finding(s), and list no more than two or three points. Conclusion: Provide a general interpretation of the results, specifying what is new/innovative of your project, and give any important recommendation for future research.Once you've written these, delete the keywords, edit for flow, and you have your abstract. \vspace{1em}

    % Keywords
    \noindent {\textbf{Keywords}\\
    pick, 3-5, good, keywords}
\end{abstract} \vspace{1em}

% Introduction
\section{Introduction}
Before we get to the actual introduction, welcome to Overleaf, as well as \LaTeX\ itself! Although \LaTeX certainly has its quirks, we hope that by contrasting the template you see here with the compiled document on the right side, you can get an intuitive sense of how to work with it. Anyhow, let's begin!

@@

% Materials and Methods
\section{Materials \& Methods}

This is where you talk about the methods used to carry out the study. Be as concise and to-the-point as possible, and remember - \textbf{do not justify your methods here!} You simply need to state what you did. You can (and probably should) mention the purpose of using a certain computational tool within the context of what you set out to achieve, but mentioning things like 'it's particularly efficient at this and better than all competing computational tools' is unnecessary in the methods section. However, you can definitely talk about all of this in the discussion, and talk about why your methods are, say, the most effective ones for the task.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{figures/test.png}
  \caption{Notice how \LaTeX\ automatically numbers this figure.}
\end{figure}

% Discussion
\section{Discussion}
And here is the 'meat' of the paper, so to speak. This is where you interpret your results, pointing out interesting trends within your data and how they relate to your initial hypothesis. This is also the place to justify your methodology, if you're so inclined (i.e. Why did you specifically use a certain statistical test over another? Why this tool over that tool?). Lastly, you're going to want to discuss potential sources of error. Make sure to make explicit reference to figures/tables when discussing your data; it can be helpful to walk the reader through your own personal interpretation of each figure in order. Although we recommend looking at past winning papers over at the STEM Fellowship Journal's website anyways, referring to those papers might prove most helpful when it comes to writing your discussion.

>>>>

\documentclass[10pt, twocolumn, letterpaper]{article}

@@

% Abstract
\begin{abstract}
    Your abstract will get published whether or not your team wins the challenge, so make sure to do a good job! It should reflect the objectives, methodology and findings of the research project. When writing your abstract, choose the right (amount of) words to convey your information. Avoid long sentences and long-winded explanations as they could make the reader lose focus. The order of your writing is also important. Maintain a logical order to your writing so that the reader links each aspect of your work coherently. Introduction/Background: Explains what problem the study examined and why. You may provide some background to the project, and the motivation behind it. Materials and Methods: Describes the data sources used and methodologies adopted for the data analysis. Key Findings/Results: Outlines the discoveries/what was observed from the analysis. When describing your results, strive to focus on the main finding(s), and list no more than two or three points. Conclusion: Provide a general interpretation of the results, specifying what is new/innovative of your project, and give any important recommendation for future research.Once you've written these, delete the keywords, edit for flow, and you have your abstract.
\end{abstract} \vspace{1em}

% Keywords
\noindent {\textbf{Keywords}\\
pick, 3-5, good, keywords}

% Introduction
\section{Introduction}
Before we get to the actual introduction, welcome to Overleaf, as well as \LaTeX\ itself! Although \LaTeX\ certainly has its quirks, we hope that by contrasting the template you see here with the compiled document on the right side, you can get an intuitive sense of how to work with it. Anyhow, let's begin!

@@

% Materials and Methods
\section{Materials \& Methods}
This is where you talk about the methods used to carry out the study. Be as concise and to-the-point as possible, and remember - \textbf{do not justify your methods here!} You simply need to state what you did. You can (and probably should) mention the purpose of using a certain computational tool within the context of what you set out to achieve, but mentioning things like 'it's particularly efficient at this and better than all competing computational tools' is unnecessary in the methods section. However, you can definitely talk about all of this in the discussion, and talk about why your methods are, say, the most effective ones for the task.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{Figures/test.png}
  \caption{Notice how \LaTeX\ automatically numbers this figure.}
\end{figure}

% Discussion
\section{Discussion}
And here is the 'meat' of the paper, so to speak. This is where you interpret your results, pointing out interesting trends within your data and how they relate to your initial hypothesis. This is also the place to justify your methodology, if you're so inclined (i.e. Why did you specifically use a certain statistical test over another? Why this tool over that tool?). Lastly, you're going to want to discuss potential sources of error. Make sure to make explicit reference to Figures/tables when discussing your data; it can be helpful to walk the reader through your own personal interpretation of each figure in order. Although we recommend looking at past winning papers over at the STEM Fellowship Journal's website anyways, referring to those papers might prove most helpful when it comes to writing your discussion.
